### 2014-01-24 rscripts/manuscript.Rnw
changes + compiled diff

The simulation runner sends \texttt{Time(t:Long)} messages to all actors in the simulation to indicate the march of time.  In general, during each time step a leader may initiate a new \texttt{Bad} message.  Other members of the covert group circulate \texttt{Bad} messages subsequent to receiving a \texttt{Bad} message themselves, with different probabilities for sending messages to superiors, collaborators, and subordinates.  Those probabilities do not depend on the origin of the received message (though this could be a useful mechanical tweak to the model).

Though those probabilities could be coded into the actors

>>>>

The simulation runner sends \texttt{Time(t:Long)} messages to all actors in the simulation to indicate the march of time (waiting for them to complete all their business for that step and reply with \texttt{TimeAck(t)}).  In general, during each time step a leader may initiate a new \texttt{Bad} message.  Other members of the covert group circulate \texttt{Bad} messages subsequent to receiving a \texttt{Bad} message themselves, with different probabilities for sending messages to superiors, collaborators, and subordinates.  Those probabilities do not depend on the origin of the received message (though this could be a useful mechanical tweak to the model).

Though those probabilities could be coded into the actors as part of their initialization, if they are set and adjusted by events then the actors (i) more accurrately reflect real behavior and (ii) the evolution of individuals occurs via a consistent simulation mechanism.  The former provides a lever for expert insight and empirical study.  The latter makes it easier to produce real-alike data -- i.e., simulation data that has the form of real observations.

In our simplified example, we do not consider how ``real'' events would translate into adjusting a covert member's behavior.  Instead, the simulation runner sends a message, giving us a wedge for later adjustment without frontloading too much model complexity.  This represents the final step (in our simulation) for how the plotters evolve in state, so the following repeats the previous snippets with some condensing modifications to the code

\begin{code}
object SimActor {
// the companion object, where we define common elements for SimActors
  case class Radicalize(id:Long)  // become a plotter
  case class Collaboration(id:Long, group:Set[Plotter])
                                  // link existing plotters
  case class Subordinates(id:Long, recruits:Set[Plotter])
                                  // tell a plotter to recruit subordinates
  case class Recruit(id:Long)     // tell an actor to join plotters
  case class RecruitAck(id:Long)  // acknowledge recruitment
  type Plotter = SimActor
  type Probability = Double
}

class SimActor extends Actor {

  def plotter(
    superiors:Set[Plotter] = Set.empty,
    collaborators:Set[Plotter] = Set.empty,
    subordinates:Set[Plotter] = Set.empty,
    initiate:Probability = 0.0,     // prob. of starting plot comms
    report:Probability = 0.0,       // prob. of reporting to superiors
    collaborate:Probability = 0.0,  // prob. of working w/ peers
    delegate:Probability = 0.0      // prob. of delegating work
    ) = {
      def update(
        newSuperiors:Set[Plotter] = superiors,
        newCollaborators:Set[Plotter] = collaborators,
        newSubordinates:Set[Plotter] = subordinates,
        newInitiate:Probability = initiate,
        newReport:Probability = report,
        newCollaborate:Probability = collaborate,
        newDelegate:Probability = delegate
        ) = {
          context become plotter(newSuperiors, newCollaborators, newSubordinates,
            newInitiate, newReport, newCollaborate, newDelegate)
      }

      {
        case Subordinates(_, recruits) =>
          recruits foreach { recruit =>
            recruit ! Recruit(0)
          }
        case RecruitAck(_) => update(newSubordinates = subordinates + sender)
        // ... other cases
      }
  }
}
\end{code}
